\section{Proverb 26 Outlines}

\subsection{My Outlines}

\subsubsection{Character of a Fool}
\textbf{Introduction: } There are distinguishing traits of fools. They are changeable, but if one never gets rid of these, he has marked himself:
\index[speaker]{Keith Anthony!Proverb 26 (Character of a Fool)}
\index[series]{Proverbs (Keith Anthony)!Pro 26 (Character of a Fool)}
\index[date]{2016/05/19!Proverb 26 (Character of a Fool) (Keith Anthony)}
\begin{compactenum}[I.]
    \item \textbf{Uncorrected} \index[scripture]{Proverbs!Pro 26:04}(Pro 26:4) -- one that stays uncorrected, and even worse is proud of that
    \item \textbf{Unreliable} \index[scripture]{Proverbs!Pro 26:06}(Pro 26:6)
    \item \textbf{Unteachable} \index[scripture]{Proverbs!Pro 26:07, 09}(Pro 26:7, 9)
    \item \textbf{Unworthy} \index[scripture]{Proverbs!Pro 26:08}(Pro 26:8) -- of course, we are ultimately all unworthy, but if nothing worthy of praise emerges in a life then perhaps ...
    \item \textbf{Unchangeable} \index[scripture]{Proverbs!Pro 26:11}(Pro 26:11)
    \item \textbf{Unmotivated} \index[scripture]{Proverbs!Pro 26:15}(Pro 26:15)
    \item \textbf{Uncaring} \index[scripture]{Proverbs!Pro 26:28}(Pro 26:28)
\end{compactenum}


\subsubsection{The Castles of Conceit}
\textbf{Introduction: } The rich, powerful, highly educated: \\
see \href{https://www.skywardcoaching.com/single-post/2016/07/13/the-seven-habits-of-highly-uncoachable-people}{The Seven Habits of Highly Un/Coachable People}. Plenty of scriptural examples, such as, Pharaoh, Saul, Nabal, and anyone who rejects the gospel ...
\index[speaker]{Keith Anthony!Proverb 26 (The Castles of Conceit)}
\index[series]{Proverbs (Keith Anthony)!Pro 26 (The Castles of Conceit)}
\index[date]{2016/05/19!Proverb 26 (The Castles of Conceit) (Keith Anthony)}
\begin{compactenum}[I.][7]
    \item Think themselves \textbf{Invulnerable and Indestructible} %\index[scripture]{Proverbs!Pro 26:04}(Pro 26:4) -- one that stays uncorrected, and even worse is proud of that
    \item Think themselves \textbf{Impressive}
    \item Think themselves \textbf{Indispensible}
    \item Acts \textbf{Independent} (from God and truth)
    \item Are \textbf{Incorrigible}
    \item Are \textbf{Impetuous} (uncoachable and uncorrectible)
    \item Instead are \textbf{Insecure \& Insubstantial}\\
\end{compactenum}
\begin{compactenum}[1.][7]
    \item Certainty vs. Ambiguity
    \item Expert vs. Beginner’s Mindset
    \item Entitlement vs. Gratitude
    \item Perfection vs. Practice
    \item Blame vs. Accountability
    \item Intent vs. Impact
    \item Talking vs. Listening
\end{compactenum}
