\subsection{Oultines from Eades}

\subsubsection{When People Get What's Coming to Them}
\index[speaker]{Brian Eades!Proverb 24:17-18 (When People Get What's Coming to Them)}
\index[series]{Proverbs (Brian Eades)!Proverb 24:17-18 (When People Get What's Coming to Them)}
\index[date]{2018/11/1!Proverb 24:17-18 (When People Get What's Coming to Them) (Brian Eades)}
\begin{compactenum}[I.][5]
    \item \textbf{Do Not Rejoice} - a good example of this is King David when he was chased for 10 years by King Saul. When the wicked King died and everyone else celebrated and said that he got what was coming to him, David remained humble and mourned for his enemy.\footnote{Brian Eades, 1 Nov 2018, Sermon Hints Group}
    \item \textbf{Do Not Repeat} - It's wrong for you to get joy out of anothers sorrow, and it is double the wrong if you gossip about it to others to make yourself look good. We should never have the attitude of ``I told you so.'' Jesus told us to love our enemies and to bless those that curse us and despitefully use us. Nowhere are we told in the Bible to hope that something bad happens to someone else.
    \item \textbf{Do Not Reward Yourself} - Often it is not what happens to others that is their test, but rather what happens to them maybe a test on your reaction! We are told in this text that God watches your behavior when your enemy Falls.
\end{compactenum}

\index[FACEBOOK]{SERMON HINTS!Brian Eades (When People Get What's Coming to Them) - Proverb 24:17-18!2018/11/1}


%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{When the Going Gets Tough, the Tough Get Going}
\textbf{Introduction:} Fainting is a scary thing if it's ever happened to you. First there is a lack of control and things get dark and your breathing is labored. The next thing you know you are unconscious what's really going on around you. The real test of Christianity in this life is how we hold up in hard times. That is the story of Faith throughout the Bible. Hebrews 11 is a great example of people that did not faint in adversity. As Paul once said, they read you like a book.  All true faith is tested at one time or another.\\
\index[speaker]{Brian Eades!Proverb 24:10-12 (When the Going Gets Tough, the Tough Get Going)}
\index[series]{Proverbs (Brian Eades)!Proverb 24:10-12 (When the Going Gets Tough, the Tough Get Going)}
\index[date]{2018/11/2!Proverb 24:10-12 (When the Going Gets Tough, the Tough Get Going) (Brian Eades)}
\begin{compactenum}[I.][5]
    \item \textbf{Adversity in the Form of Outward Trouble} - Most of the time what happens outside of us is beyond our control. Yes we can face the consequences of our sins on the outside, but for the most part this has to do with circumstances that are adverse.\footnote{Brian Eades, 2 Nov 2018, Sermon Hints Group}
    \item \textbf{Adversity in the Form of Inward Thoughts} - Verse 12 gives us the illustration of when we say we don't know what's going on and we really do in our minds. This is the story of someone who knows what to do but doesn't do it..... The sin of omission. God knows our thoughts and we cannot hide them from him. Recently scientist have been able to inject people with chemicals to the point that they can see certain dreams with an MRI machine and a certain type of software to decipher the electronic field. I would hate to think what would happen if men could read our minds completely, but God is more important than he already knows.
    \item \textbf{Adversity in the Form of Downward Trends} - The very thing that proves the weakness in my spiritual life is when I backslide and move downward in my faith.  Forgiveness of others, loving the Brethren, not forsaking the assembling of ourselves together, works and charity are all evidences for a believer that they are somewat level in their faith, as opposed to going downward.
    \item \textbf{Adversity that Causes and Upward Turn} - The Psalmist said, I will look up and lift up mine eyes unto the hills from whence cometh my help, my help comes from the Lord that made Heaven and the Earth.
\end{compactenum}

\index[FACEBOOK]{SERMON HINTS!Brian Eades (When the Going Gets Tough, the Tough Get Going) - Proverb 24:10-12!2018/11/2}


%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Get Back Up! or The Comeback Kid}
\textbf{Introduction:} Nothing sets a precedent for Christianity more than people that are great comeback stories!  We could talk about Joseph, King David, and numerous other heroes of Faith, but God is interested in your life and mine before today's generation as examples of God's power and Grace. The latter part of the scripture warns believers not to rejoice when wicked people "get what's coming".  In fact, we will be shedding tears at the great white throne judgment when the lost are thrown into the Lake of fire.  The wages of sin and the fall of humanity is not something to celebrate in any way. Everyone falls and fails in life,  but the difference between Christians and lost people is that we have Christ to pull us up out of the miry clay and set us on a rock, and establish our goings, and to put a song in our heart and lips. It is a shame when people say that they are believers, but they lay around and whine all the time about their problems instead of being a bright shining example of the grace of God. As I get older I am discovering that falling can do a lot of damage physically.  The old commercial where the woman falls and touches her Life alert necklace to screams,  "I have fallen and I can't get up"....well I used to laugh at that commercial until I took a fall myself. I fell on my knee, and it still hurts a year later! Here are 7 falls and risings of the saints:\\
\index[speaker]{Brian Eades!Proverb 24:16-18 (Get Back Up! or The Comeback Kid)}
\index[series]{Proverbs (Brian Eades)!Proverb 24:16-18 (Get Back Up! or The Comeback Kid)}
\index[date]{2019/06/20!Proverb 24:16-18 (Get Back Up! or The Comeback Kid) (Brian Eades)}
\begin{compactenum}[I.][5]
    \item \textbf{Financial Recovery} - The widow's mite story is evidence that it's not about money when it comes to our survival anyway, it is about our faith.  The world tells you that you need money to survive but God says the contrary.\footnote{Brian Eades, 20 June 2019, Sermon Hints Group}
    \item \textbf{Family Recovery} - Job is a bright shining example that when you lose everything precious to you thank God can give you something in its place.
    \item \textbf{Fault Recovery} - David speaks volumes in Psalm 51 about recovery from the brokenness of his sins.
    \item \textbf{Faith Recovery} - Many saints can become so discouraged with life that they get out of church, stop praying,  and lose sight of what God has done for them. Moses is a bright example of "faith recovery" overtime while he was in the wilderness.
    \item \textbf{Physical Recovery} - Health problems can make you despair of life, and want to lay on the ground until you die, but "there is lifting up" when you get down.  For all of us we are just one diagnosis from severe depression, but I'm glad the Lord can lift people up  and give them grace when they are facing the surgeon's knife; I know this because I have been there and done that!  I have heard the doctor mention the possibility of the "c" word in a scheduled surgery on my abdomen!  I used to pray over people having surgeries all the time and told them the Lord would be with them, and then the Lord put me on my back four different times to be cut on.  NOW I KNOW when I pray for people about falling down and getting back up myself! See Job 22:29.
    \item \textbf{Future Recovery} - One of the best healers is time.  Solomon himself speaks the progression of time and all of our lives in Ecclesiastes 3, and says that God "makes everything beautiful in his time". You see, getting up is not always something that occurs quickly, so give the Lord sometime to work things in your life. Most of us have preached that simple sermon on prayer by explaining to people that God answers ALL prayer: SOME PRAYERS ARE DENIED, ANSWERED DIFFERENTLY, ANSWERED DIRECTLY, OR ELSE DELAYED UNTIL THE FUTURE..... So if you are on the ground spiritually, and have prayed for many years, just keep praying and he will get you up one way or another.
    \item \textbf{Failure to Recover} - There is no excuse for not recovering as a child of God. You must ask yourself are you a true believer? Paul said I can do all things through Christ which strengthens me. Quit laying on the ground and realize who stands beside you!
\end{compactenum}

\index[FACEBOOK]{SERMON HINTS!Brian Eades (Get Back Up, or The Comeback Kid) - Proverb 24:16-18!2019/06/20}



%%%%%%%%%%%%%%%%%%%%
\subsubsection{The Importance of Getting Back Up}
\textbf{Introduction:} When I was a child we had a saying, if it first you don't succeed try try again!  Being a musician requires many failures and frustrations to get things right with any instrument. Being an athlete requires years of discipline and failure, but the heroes and the great songs of our day are sung by people who got back up.
It is interesting that Solomon mentions falling seven times but only Rising one time. In our lives it seems like we fall more than we rise, but the important thing is that we get back up. When I lived in Los Angeles there were times that I got into fights with other kids. These fights could be bloody fights, but I was told to get back up and not just lay there. You see, when you get knocked down if you lay there, the enemy will just kick you and kick you. On the other hand if a grizzly bear is attacking you they tell you to just play dead, but the objective is so the bear will go away and eventually you will get back up.\\
\index[speaker]{Brian Eades!Proverb 24:16 (The Importance of Getting Back Up)}
\index[series]{Proverbs (Brian Eades)!Proverb 24:16 (The Importance of Getting Back Up)}
\index[date]{2019/11/2!Proverb 24:16 (The Importance of Getting Back Up) (Brian Eades)}
\begin{compactenum}[I.][5]
    \item \textbf{Our Loss of Grip} \footnote{Brian Eades, 2 November 2018, Sermon Hints Group}
    \item \textbf{Our Life on the Ground} 
    \item \textbf{Our Lift from God}
\end{compactenum}

\index[FACEBOOK]{SERMON HINTS!Brian Eades (The Importance of Getting Back Up) - Proverb 24:16!2019/11/2}

    
    
