\chapter{Deuteronomy 6}

\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{WHAT GOD REALLY WANTS}}\\ (Deuteronomy 6:1-25) \begin{compactenum}[I.][8]
    \item Men to  \textbf{Teach} of Him \index[scripture]{Deuteronomy!Deu 06:01}\index[scripture]{Deuteronomy!Deu 06:07}  (Deu 6:1, 7)
    \item Men to  \textbf{Obey} Him \index[scripture]{Deuteronomy!Deu 06:02} \index[scripture]{Deuteronomy!Deu 06:03}\index[scripture]{Deuteronomy!Deu 06:06}\index[scripture]{Deuteronomy!Deu 06:25} (Deu 6:2, 3, 6, 25)
    \item Men to  \textbf{Love} Him \index[scripture]{Deuteronomy!Deu 06:05}  (Deu 6:5)
    \item Men to  \textbf{Walk} with Him \index[scripture]{Deuteronomy!Deu 06:07}  (Deu 6:7)
    \item Men to  \textbf{Fear} Him \index[scripture]{Deuteronomy!Deu 06:13}  (Deu 6:13)
    \item Men to  be \textbf{Faithful} to Him \index[scripture]{Deuteronomy!Deu 06:13}  (Deu 6:13)
    \item Men to   \textbf{Recall} His Works \index[scripture]{Deuteronomy!Deu 06:21--25}  (Deu 6:21--25)
\end{compactenum}}



\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/deuteronomy_6.html}{\textcolor[cmyk]{0.99998,1,0,0}{Deuteronomy 6 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{Now these \emph{are} the commandments, the statutes, and the judgments, which the LORD your God commanded \fcolorbox{bone}{bone}{to} \fcolorbox{bone}{lime}{teach} you, that ye might do \emph{them} in the land whither ye go \fcolorbox{bone}{bone}{to} possess it:}
[2] \textcolor[cmyk]{0.99998,1,0,0}{That thou mightest fear the LORD thy God, \fcolorbox{bone}{bone}{to} \fcolorbox{bone}{lime}{keep} all his statutes and his commandments, which I command  \fcolorbox{bone}{bone}{thee}, thou, and thy son, and thy son's son, all the days of thy life; and that thy days may be prolonged.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{Hear therefore, O Israel, and \fcolorbox{bone}{lime}{observe} \fcolorbox{bone}{bone}{to} do \emph{it}; that it may be well with  \fcolorbox{bone}{bone}{thee}, and that ye may increase mightily, as the LORD God of thy fathers hath promised  \fcolorbox{bone}{bone}{thee}, in the land that floweth with milk and honey.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{Hear, O Israel: The LORD our God \emph{is} one LORD:}
[5] \textcolor[cmyk]{0.99998,1,0,0}{And thou shalt \fcolorbox{bone}{lime}{love the LORD thy God} with all thine heart, and with all thy soul, and with all thy might.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{And these words, which I command  \fcolorbox{bone}{bone}{thee} this day, shall be \fcolorbox{bone}{lime}{in thine heart}:}
[7] \textcolor[cmyk]{0.99998,1,0,0}{And thou shalt \fcolorbox{bone}{lime}{teach} them diligently unto thy children, and shalt talk of them when thou sittest in thine house, and when thou \fcolorbox{bone}{lime}{walkest} by the way, and when thou liest down, and when thou risest up.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{And thou shalt bind them for a sign upon thine hand, and they shall be as frontlets between thine eyes.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{And thou shalt write them upon the posts of thy house, and on thy gates.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{And it shall be, when the LORD thy God shall have brought  \fcolorbox{bone}{bone}{thee} into the land which he sware unto thy fathers, \fcolorbox{bone}{bone}{to} Abraham, \fcolorbox{bone}{bone}{to} Isaac, and \fcolorbox{bone}{bone}{to} Jacob, \fcolorbox{bone}{bone}{to} give  \fcolorbox{bone}{bone}{thee} great and goodly cities, which thou buildedst not,}
[11] \textcolor[cmyk]{0.99998,1,0,0}{And houses full of all good \emph{things}, which thou filledst not, and wells digged, which thou diggedst not, vineyards and olive trees, which thou plantedst not; when thou shalt have eaten and be full;}
[12] \textcolor[cmyk]{0.99998,1,0,0}{\emph{Then} beware lest thou forget the LORD, which brought  \fcolorbox{bone}{bone}{thee} forth out of the land of Egypt, from the house of bondage.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{Thou shalt \fcolorbox{bone}{lime}{fear} the LORD thy God, and serve him, and shalt \fcolorbox{bone}{lime}{swear by his name}.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{Ye shall not go after other gods, of the gods of the people which \emph{are} round about you;}
[15] \textcolor[cmyk]{0.99998,1,0,0}{(For the LORD thy God \emph{is} a jealous God among you) lest the anger of the LORD thy God be kindled against  \fcolorbox{bone}{bone}{thee}, and destroy  \fcolorbox{bone}{bone}{thee} from off the face of the earth.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{Ye shall not tempt the LORD your God, as ye tempted \emph{him} in Massah.}\footnote{\textbf{Exodus 17:2-7} - Wherefore the people did chide with Moses, and said, Give us water that we may drink. And Moses said unto them, Why chide ye with me? wherefore do ye tempt the LORD? [3] And the people thirsted there for water; and the people murmured against Moses, and said, Wherefore is this that thou hast brought us up out of Egypt, to kill us and our children and our cattle with thirst? [4] And Moses cried unto the LORD, saying, What shall I do unto this people? they be almost ready to stone me. [5] And the LORD said unto Moses, Go on before the people, and take with thee of the elders of Israel; and thy rod, wherewith thou smotest the river, take in thine hand, and go. [6] Behold, I will stand before thee there upon the rock in Horeb; and thou shalt smite the rock, and there shall come water out of it, that the people may drink. And Moses did so in the sight of the elders of Israel. [7] And he called the name of the place Massah, and Meribah, because of the chiding of the children of Israel, and because they tempted the LORD, saying, Is the LORD among us, or not?}
[17] \textcolor[cmyk]{0.99998,1,0,0}{Ye shall diligently keep the commandments of the LORD your God, and his testimonies, and his statutes, which he hath commanded  \fcolorbox{bone}{bone}{thee}.}
[18] \textcolor[cmyk]{0.99998,1,0,0}{And thou shalt do \emph{that} \emph{which} \emph{is} right and good in the sight of the LORD: that it may be well with  \fcolorbox{bone}{bone}{thee}, and that thou mayest go in and possess the good land which the LORD sware unto thy fathers,}
[19] \textcolor[cmyk]{0.99998,1,0,0}{To cast out all thine enemies from before  \fcolorbox{bone}{bone}{thee}, as the LORD hath spoken.}
[20] \textcolor[cmyk]{0.99998,1,0,0}{\emph{And} when thy son asketh  \fcolorbox{bone}{bone}{thee} in time \fcolorbox{bone}{bone}{to} come, saying, What \emph{mean} the testimonies, and the statutes, and the judgments, which the LORD our God hath commanded you?}
[21] \textcolor[cmyk]{0.99998,1,0,0}{Then thou shalt say unto thy son, We were Pharaoh's bondmen in Egypt; and \fcolorbox{bone}{lime}{the LORD brought us out} of Egypt with a mighty hand:}
[22] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD shewed signs and wonders, great and sore, upon Egypt, upon Pharaoh, and upon all his household, before our eyes:}
[23] \textcolor[cmyk]{0.99998,1,0,0}{And he brought us out from thence, that he might bring us in, \fcolorbox{bone}{bone}{to} give us the land which he sware unto our fathers.}
[24] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD commanded us \fcolorbox{bone}{bone}{to} do all these statutes, \fcolorbox{bone}{bone}{to} fear the LORD our God, for our good always, that he might preserve us alive, as \emph{it} \emph{is} at this day.}
[25] \textcolor[cmyk]{0.99998,1,0,0}{And it shall be our \fcolorbox{bone}{MYGOLD}{righteousness}, if we \fcolorbox{bone}{lime}{observe} \fcolorbox{bone}{bone}{to} do all these commandments before the LORD our God, as he hath commanded us.}
