\chapter{Deuteronomy 3}
\footnote{\textcolor[rgb]{0.00,0.25,0.00}{\hyperlink{DeuteronomyTOC}{Return to end of Table of Contents.}}}\textcolor[rgb]{0.00,0.00,1.00}{Then we turned, and went up the way to Bashan: and Og the king of Bashan came out against us, he and all his people, to battle at Edrei.}
[2] \textcolor[rgb]{0.00,0.00,1.00}{And the LORD said unto me, Fear him not: for I will deliver him, and all his people, and his land, into thy hand; and thou shalt do unto him as thou didst unto Sihon king of the Amorites, which dwelt at Heshbon.}
[3] \textcolor[rgb]{0.00,0.00,1.00}{So the LORD our God delivered into our hands Og also, the king of Bashan, and all his people: and we smote him until none was left to him remaining.}
[4] \textcolor[rgb]{0.00,0.00,1.00}{And we took all his cities at that time, there was not a city which we took not from them, threescore cities, all the region of Argob, the kingdom of Og in Bashan.}
[5] \textcolor[rgb]{0.00,0.00,1.00}{All these cities \emph{were} fenced with high walls, gates, and bars; beside unwalled towns a great many.}
[6] \textcolor[rgb]{0.00,0.00,1.00}{And we utterly destroyed them, as we did unto Sihon king of Heshbon, utterly destroying the men, women, and children, of every city.}
[7] \textcolor[rgb]{0.00,0.00,1.00}{But all the cattle, and the spoil of the cities, we took for a prey to ourselves.}
[8] \textcolor[rgb]{0.00,0.00,1.00}{And we took at that time out of the hand of the two kings of the Amorites the land that \emph{was} on this side Jordan, from the river of Arnon unto mount Hermon;}
[9] \textcolor[rgb]{0.00,0.00,1.00}{(\emph{Which} Hermon the Sidonians call Sirion; and the Amorites call it Shenir;)}
[10] \textcolor[rgb]{0.00,0.00,1.00}{All the cities of the plain, and all Gilead, and all Bashan, unto Salchah and Edrei, cities of the kingdom of Og in Bashan.}
[11] \textcolor[rgb]{0.00,0.00,1.00}{For only Og king of Bashan remained of the remnant of giants; behold, his bedstead \emph{was} a bedstead of iron; \emph{is} it not in Rabbath of the children of Ammon? nine cubits \emph{was} the length thereof, and four cubits the breadth of it, after the cubit of a man.}
[12] \textcolor[rgb]{0.00,0.00,1.00}{And this land, \emph{which} we possessed at that time, from Aroer, which \emph{is} by the river Arnon, and half mount Gilead, and the cities thereof, gave I unto the Reubenites and to the Gadites.}
[13] \textcolor[rgb]{0.00,0.00,1.00}{And the rest of Gilead, and all Bashan, \emph{being} the kingdom of Og, gave I unto the half tribe of Manasseh; all the region of Argob, with all Bashan, which was called the land of giants.}
[14] \textcolor[rgb]{0.00,0.00,1.00}{Jair the son of Manasseh took all the country of Argob unto the coasts of Geshuri and Maachathi; and called them after his own name, Bashan-havoth-jair, unto this day.}
[15] \textcolor[rgb]{0.00,0.00,1.00}{And I gave Gilead unto Machir.}
[16] \textcolor[rgb]{0.00,0.00,1.00}{And unto the Reubenites and unto the Gadites I gave from Gilead even unto the river Arnon half the valley, and the border even unto the river Jabbok, \emph{which is} the border of the children of Ammon;}
[17] \textcolor[rgb]{0.00,0.00,1.00}{The plain also, and Jordan, and the coast \emph{thereof}, from Chinnereth even unto the sea of the plain, \emph{even} the salt sea, under Ashdoth-pisgah eastward.}\\
\\
\P \textcolor[rgb]{0.00,0.00,1.00}{And I commanded you at that time, saying, The LORD your God hath given you this land to possess it: ye shall pass over armed before your brethren the children of Israel, all \emph{that are} meet for the war.}
[19] \textcolor[rgb]{0.00,0.00,1.00}{But your wives, and your little ones, and your cattle, (\emph{for} I know that ye have much cattle,) shall abide in your cities which I have given you;}
[20] \textcolor[rgb]{0.00,0.00,1.00}{Until the LORD have given rest unto your brethren, as well as unto you, and \emph{until} they also possess the land which the LORD your God hath given them beyond Jordan: and \emph{then} shall ye return every man unto his possession, which I have given you.}\\
\\
\P \textcolor[rgb]{0.00,0.00,1.00}{And I commanded Joshua at that time, saying, Thine eyes have seen all that the LORD your God hath done unto these two kings: so shall the LORD do unto all the kingdoms whither thou passest.}
[22] \textcolor[rgb]{0.00,0.00,1.00}{Ye shall not fear them: for the LORD your God he shall fight for you.}
[23] \textcolor[rgb]{0.00,0.00,1.00}{And I besought the LORD at that time, saying,}
[24] \textcolor[rgb]{0.00,0.00,1.00}{O Lord GOD, thou hast begun to shew thy servant thy greatness, and thy mighty hand: for what God \emph{is there} in heaven or in earth, that can do according to thy works, and according to thy might?}
[25] \textcolor[rgb]{0.00,0.00,1.00}{I pray thee, let me go over, and see the good land that \emph{is} beyond Jordan, that goodly mountain, and Lebanon.}
[26] \textcolor[rgb]{0.00,0.00,1.00}{But the LORD was wroth with me for your sakes, and would not hear me: and the LORD said unto me, Let it suffice thee; speak no more unto me of this matter.}
[27] \textcolor[rgb]{0.00,0.00,1.00}{Get thee up into the top of Pisgah, and lift up thine eyes westward, and northward, and southward, and eastward, and behold \emph{it} with thine eyes: for thou shalt not go over this Jordan.}
[28] \textcolor[rgb]{0.00,0.00,1.00}{But charge Joshua, and encourage him, and strengthen him: for he shall go over before this people, and he shall cause them to inherit the land which thou shalt see.}
[29] \textcolor[rgb]{0.00,0.00,1.00}{So we abode in the valley over against Beth-peor.}
\newpage
