\chapter{Psalm 55}

\marginpar{\scriptsize \centering \fcolorbox{black}{lime}{\textbf{DAVID'S DELIVERANCE}}\\ (Psalm 55:1-23) \begin{compactenum}[I.][8]
    \item \textbf{Fear} \index[scripture]{Psalms!Psa 055:04}(Psa 55:4)
    \item \textbf{Flight} \index[scripture]{Psalms!Psa 055:06}(Psa 55:6)
    \item David's \textbf{Fantasy} (to run from trouble) \index[scripture]{Psalms!Psa 055:06}(Psa 55:6)
    \item The \textbf{Foe} \index[scripture]{Psalms!Psa 055:13}(Psa 55:13)
    \item \textbf{Footprints} (of Evil) \index[scripture]{Psalms!Psa 055:13}(Psa 55:13) -- 13 words in verse 13 (One of those signature verses in scripture)
    \item A \textbf{Forsaking} (the covenant breaker and a broken covenant, as with the Antchrist) \index[scripture]{Psalms!Psa 055:19}(Psa 55:19)
    \item \textbf{Faithfulness} (Of God to deliver David and to deliver a people in the Great Tribualtion) \index[scripture]{Psalms!Psa 055:23}(Psa 55:23)
\end{compactenum}}


\footnote{\textcolor[rgb]{0.00,0.25,0.00}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/psalms_55.html}{\textcolor[cmyk]{0.99998,1,0,0}{Psalm 55 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{To the chief Musician on Neginoth, Maschil, \emph{A Psalm} of David.}\\
\\
\textcolor[cmyk]{0.99998,1,0,0}{Give ear to my prayer, O God; and hide not thyself from my supplication.}\footnote{\textbf{Psalm 5:1} - Give ear to my words, O LORD, consider my meditation.}\footnote{\textbf{Psalm 17:1} -  Hear the right, O LORD, attend unto my cry, give ear unto my prayer, that goeth not out of feigned lips.}\footnote{\textbf{Psalm, 64:1} - Hear my voice, O God, in my prayer: preserve my life from fear of the enemy.}\footnote{\textbf{Psalm 80:1} - Give ear, O Shepherd of Israel, thou that leadest Joseph like a flock; thou that dwellest between the cherubims, shine forth.}\footnote{\textbf{Psalm 84:8} - O LORD God of hosts, hear my prayer: give ear, O God of Jacob. Selah.}\footnote{\textbf{1 Peter 3:12} - For the eyes of the Lord are over the righteous, and his ears are open unto their prayers: but the face of the Lord is against them that do evil.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{Attend unto me, and hear me: I mourn in my complaint, and make a noise;}\footnote{\textbf{Psalm 32:3} - When I kept silence, my bones waxed old through my roaring all the day long.}\footnote{\textbf{Psalm 38:6} - I am troubled; I am bowed down greatly; I go mourning all the day long.}\footnote{\textbf{Psalm 43:2} - For thou art the God of my strength: why dost thou cast me off? why go I mourning because of the oppression of the enemy?}\footnote{\textbf{Isaiah 38:14} - Like a crane or a swallow, so did I chatter: I did mourn as a dove: mine eyes fail with looking upward: O LORD, I am oppressed; undertake for me.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{Because of the voice of the enemy, because of the oppression of the wicked: for they cast iniquity upon me, and in wrath they hate me.}\footnote{\textbf{Psalm 12:5} - For the oppression of the poor, for the sighing of the needy, now will I arise, saith the LORD; I will set him in safety from him that puffeth at him.}\footnote{\textbf{Psalm 54:3} - For strangers are risen up against me, and oppressors seek after my soul: they have not set God before them. Selah.}\footnote{\textbf{Psalm 73:8} - They are corrupt, and speak wickedly concerning oppression: they speak loftily.}\footnote{\textbf{Psalm 27:12} - Deliver me not over unto the will of mine enemies: for false witnesses are risen up against me, and such as breathe out cruelty.}\footnote{\textbf{Psalm 35:11} - False witnesses did rise up; they laid to my charge things that I knew not.}\footnote{\textbf{2 Samuel 15:3} - And Absalom said unto him, See, thy matters are good and right; but there is no man deputed of the king to hear thee.}\footnote{\textbf{2 Samuel 16:7-8} - And thus said Shimei when he cursed, Come out, come out, thou bloody man, and thou man of Belial: The LORD hath returned upon thee all the blood of the house of Saul, in whose stead thou hast reigned; and the LORD hath delivered the kingdom into the hand of Absalom thy son: and, behold, thou art taken in thy mischief, because thou art a bloody man.}\footnote{\textbf{Matthew 26:59} - Now the chief priests, and elders, and all the council, sought false witness against Jesus, to put him to death;}
[4] \textcolor[cmyk]{0.99998,1,0,0}{My heart is sore pained within me: and the \fcolorbox{black}{lime}{terrors} of death are fallen upon me.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{Fearfulness and trembling are come upon me, and horror hath overwhelmed me.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{And I said, Oh that I had \fcolorbox{black}{lime}{wings} like a dove! \emph{for} \emph{then} would I \fcolorbox{black}{lime}{fly away}, and be at rest.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{Lo, \emph{then} would I wander far off, \emph{and} remain in the wilderness. Selah.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{I would hasten my escape from the windy storm \emph{and} tempest.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{Destroy, O Lord, \emph{and} divide their tongues: for I have seen violence and strife in the city.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{Day and night they go about it upon the walls thereof: mischief also and sorrow \emph{are} in the midst of it.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{Wickedness \emph{is} in the midst thereof: deceit and guile depart not from her streets.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{For \emph{it} \emph{was} not an enemy \emph{that} reproached me; then I could have borne \emph{it}: neither \emph{was} \emph{it} he that hated me \emph{that} did magnify \emph{himself} against me; then I would have hid myself from him:}
[13] \textcolor[cmyk]{0.99998,1,0,0}{But \emph{it} \emph{was} thou, \fcolorbox{black}{lime}{a man mine equal}, my guide, and \fcolorbox{black}{lime}{mine acquaintance}.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{We took sweet counsel together, \emph{and} walked unto the house of God in company.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{Let death seize upon them, \emph{and} let them go down quick into hell: for wickedness \emph{is} in their dwellings, \emph{and} among them.}
[16] \textcolor[cmyk]{0.99998,1,0,0}{As for me, I will call upon God; and the LORD shall save me.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{Evening, and morning, and at noon, will I pray, and cry aloud: and he shall hear my voice.}
[18] \textcolor[cmyk]{0.99998,1,0,0}{He hath delivered my soul in peace from the battle \emph{that} \emph{was} against me: for there were many with me.}
[19] \textcolor[cmyk]{0.99998,1,0,0}{God shall hear, and afflict them, even he that abideth of old. Selah. Because they have no changes, therefore they fear not God.}
[20] \textcolor[cmyk]{0.99998,1,0,0}{He hath put forth his hands against such as be at peace with him: he hath broken his covenant.}
[21] \textcolor[cmyk]{0.99998,1,0,0}{\emph{The} \emph{words} of his mouth were smoother than butter, but war \emph{was} in his heart: his words were softer than oil, yet \emph{were} they drawn swords.}
[22] \textcolor[cmyk]{0.99998,1,0,0}{Cast thy burden upon the LORD, and he shall sustain thee: he shall never suffer the righteous to be moved.}
[23] \textcolor[cmyk]{0.99998,1,0,0}{But thou, O God, shalt bring them down into the pit of destruction: bloody and deceitful men shall not live out half their days; but I will trust in thee.}




