\section{Psalm 53 Comments}

\subsection{Psalm 53:1}
A commentator points out that the atheist's problem is in his heart and not in his head. Any fool who has any bit of rationality will know that there has to be a God somewhere. The issue is when one does not want God to be around to interfere with what you are doing. \cite{Ruckman1992PsalmsV1}

\subsection{Psalm 53:2}
It is true, both, that people of understanding will seek God, and that by seeking God one gets understanding. God looks for the people who do seek him. It is further true that you are, and become, the things that you love and fear. Pilate feared the crowd (Matt. 27:24). Ahab feared Elijah (1 Kings 21:27). Herod feared ridicule (Matt. 14:9). Israel feared gods that were no gods (2 Kings 17:7). Judas loved money (John 12:6), as did Gehazi (2 Kings 5:20). Ahab loved property (1 Kings 21:6); Ananias and Saphirra loved a reputation for being spiritual when they weren't (Acts 5:1--4). Demas loved the present world (2 Timothy 4:10). The modern fundamentalist loves his standing among the like-minded brethren more than he loves things like scriptural truth and integrity. \cite{Ruckman1992PsalmsV1}\\
\\
\noindent In verse 2 we learn that a ``man of understanding'' will seek God by prayer, the Book, and watching and studying God’s works day and night. The terrorized people of verse 5 are terrorized because they had not called on God (vs. 4). What a man loves and what he fears are the measure of the man -- any man. No man on earth is what he professes, tolerates, stands for, makes, earns, deserves, is credited with, says, or writes. Every man on earth is what he loves and what he fears. Wisdom is simply knowing when to be afraid and when not to be afraid. ``The fear of the Lord is the beginning of wisdom'' (Prov. 9:10); ``the fear of man bringeth a snare'' (Prov. 29:25). Bob Jones III’s profession in having a ``godly institution'' that is a ``Bastion of Orthodoxy'' for ``Congresses'' of militant Fundamentalists has nothing to do with anything. If a man fears ridicule from intellectuals and loves the ``preeminent place'' as a ``defender of the faith'' he is an apostate coward. You are what you love and what you fear, and so are the other five billion inhabitants of “planet earth.”  and the Man of Sin will love POWER and WORSHIP (Dan. 11:36--38). You ARE what you love and what you fear. When a Christian educator loves property and buildings more than the souls of men, he is a carnal, worldly FOOL (Prov. 30:5, 11:30). When a Bible teacher fears the criticism of his peers and loves his own reputation as a ``great scholar,'' he is a backslidden reprobate. You are what you love and what you fear.\cite{Ruckman1992PsalmsV1}

\subsection{Psalm 53:5}
Picture the scattered bones in Ezekiel 37. With the breath of God, these bones com to life. But the passage speaks of what God does to Israel's enemies and to those who reject God, If a man fears ridicule from intellectuals and loves the ``preeminent place'' as a ``defender of the faith'' he is an apostate coward. You are what you love and what you fear, and so are the other five billion inhabitants of ``planet earth.'' Pilate feared the crowd (Matt. 27:24), Ahab feared Elijah (1 Kings 21:27), Herod feared ridicule (Matt. 14:9), and Israel feared gods that were no gods (2 Kings 17:7). Judas loved money (John 12:6), as did Gehazi (2 Kings 5:20); Ahab loved property (1 Kings 21:6); Ananias and Saphirra loved a reputation for being spiritual when they weren’t (Acts 5:1--4); and the Man of Sin will love POWER and WORSHIP (Dan. 11:36--38). What a man loves and what he fears are the measure of the man--any man. No man on earth is what he professes, tolerates, stands for, makes, earns, deserves, is credited with, says, or writes. Every man on earth is what he loves and what he fears. Wisdom is simply knowing when to be afraid and when not to be afraid. ``The fear of the Lord is the beginning of wisdom'' (Prov. 9:10); ``the fear of man bringeth a snare'' (Prov. 29:25). \cite{Ruckman1992PsalmsV1}
