\chapter{Psalm 57}



\marginpar{\scriptsize \centering \fcolorbox{black}{lime}{\textbf{GOD"S EVERYDAY ATTRIBUTES}}\\ (Psalm 57:1-22) \begin{compactenum}[I.][8]
    \item \textbf{Abundantness} 
    \item \textbf{Aboveness} 
    \item \textbf{Alongsideness} \index[scripture]{SoS!SoS 04:08}\index[scripture]{Psalms!Psa 057:11} (Psa 57:11) 
    \item \textbf{Aforeness} 
    \item \textbf{Aroundness} 
    \item \textbf{Absoluteness} 
    \item \textbf{Amongness} \index[scripture]{Matthew!Matt 18:20}(Matt 18:20) 
    \item \textbf{Awareness} 
    \item \textbf{Alwaysness} 
    \item \textbf{Attentivness}
    \item \textbf{Availability} \index[scripture]{Jeremiah!Jer 33:03} (Jer 33:3)
\end{compactenum}}



\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/psalms_57.html}{\textcolor[cmyk]{0.99998,1,0,0}{Psalm 57 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{To the chief Musician, Al-taschith, Michtam of David, when he fled from Saul in the cave.}\\
\\
\textcolor[cmyk]{0.99998,1,0,0}{Be merciful unto me, O God, be merciful unto me: for my soul trusteth in thee: yea, in the shadow of thy wings will I make my refuge, until \emph{these} calamities be overpast.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{I will cry unto God most high; unto God that performeth \emph{all} \emph{things} for me.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{He shall send from heaven, and save me \emph{from} the reproach of him that would swallow me up. Selah. God shall send forth his mercy and his truth.}\footnote{\textbf{Psalm 50:4-5} - He shall call to the heavens from above, and to the earth, that he may judge his people. 5 Gather my saints together unto me; those that have made a covenant with me by sacrifice.}\footnote{\textbf{Isaiah 26:20} - Come, my people, enter thou into thy chambers, and shut thy doors about thee: hide thyself as it were for a little moment, until the indignation be overpast.}\footnote{\textbf{Hebres 9:28} - So Christ was once offered to bear the sins of many; and unto them that look for him shall he appear the second time without sin unto salvation.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{My soul \emph{is} among lions: \emph{and} I lie \emph{even} \emph{among} them that are set on fire, \emph{even} the sons of men, whose teeth \emph{are} spears and arrows, and their tongue a sharp sword.}\footnote{\textbf{1 Peter 5:8} -  Be sober, be vigilant; because your adversary the devil, as a roaring lion, walketh about, seeking whom he may devour:}
[5] \textcolor[cmyk]{0.99998,1,0,0}{Be thou exalted, O God, above the heavens; \emph{let} thy glory \emph{be} above all the earth.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{They have prepared a net for my steps; my soul is bowed down: they have digged a pit before me, into the midst whereof they are fallen \emph{themselves}. Selah.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{My heart is fixed, O God, my heart is fixed: I will sing and give praise.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{Awake up, my glory; awake, psaltery and harp: I \emph{myself} will awake early.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{I will praise thee, O Lord, among the people: I will sing unto thee among the nations.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{For thy mercy \emph{is} great unto the heavens, and thy truth unto the clouds.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{Be thou exalted, O God, above the heavens: \emph{let} thy glory \emph{be} above all the earth.}


