\chapter{Psalm 56}


\marginpar{\scriptsize \centering \fcolorbox{black}{lime}{\textbf{O THOU MOST HIGH}}\\ (Psalm 56:1-13) \begin{compactenum}[I.][8]
    \item He \textbf{Appoints} his man on Earth \index[scripture]{Genesis!Genesis 14:18-22} (Gen 14:18-22)
    \item He \textbf{Arranges} the Affairs of History \index[scripture]{Deuteronomy!Deuteronomy 32:08} (Dt 32:8)
    \item He \textbf{Announces} his Prescence \index[scripture]{2 Samuel!2 Sameuel 22:14} (2Sa 22:14)
    \item He \textbf{Accepts} the Praise of Man \index[scripture]{Psalms!Psalm 007:17} (Psa 7:17)
    \item He \textbf{Ascends} into Heaven \index[scripture]{Isaiah!Isaiah 14:14 }(Isa 14:14)
    \item He \textbf{Appears} to Deliver \index[scripture]{Daniel!Daniel 03:26} (Dan 3:26)
    \item He is \textbf{Aware} of the Behavior of His People \index[scripture]{Psalms!Psalm 078:56} (Psa 78:56)
\end{compactenum}}

\marginpar{\scriptsize \centering \fcolorbox{black}{yellow}{\textbf{WHAT THEY DO,}} \\\fcolorbox{black}{yellow}{\textbf{WHAT I DO,}}\\ 
\fcolorbox{black}{yellow}{\textbf{WHAT GOD DOES}} \\(Psalm 56:1-13) 
\begin{compactenum}[I.][3]
    \item \textbf{What They Do}
    \begin{compactenum}[A.]
        \item They Wrest My Word (5)
        \item They Think Evil (5)
        \item They Gather Themselves (6)
        \item They Hide Themselves (6)
        \item They Mark My Steps (6)
        \item They Wait for My Soul (6)
        \item They Do Not Escape (7)
    \end{compactenum}
    \item \textbf{What I Do}
    \begin{compactenum}[A.]
       \item I Fear (3)
       \item I will trust (3, 4)
        \item I will not fear (4)
        \item I will praise (4, 10, 11, 12)
        \item I cry unto God (9)
        \item I know God is for me (9)
        \item I walk before God (12)
    \end{compactenum}    
    \item \textbf{What God Does}
    \begin{compactenum}[A.]
        \item God Delivers (13)
    \end{compactenum}
\end{compactenum}}


\marginpar{\scriptsize \centering \fcolorbox{black}{black}{\textbf{\textcolor{MYWHITE}{HELP}}} \\
(Psalm 56:1-13) 

\begin{compactenum}[I.]
    \item The \textbf{Enemies} \index[scripture]{Psalms!Psa 056:02}(Psalm 56:2) 
    \item The \textbf{Emergency} \index[scripture]{Psalms!Psa 056:03}(Psalm 56:3) 
    \item The \textbf{Expression} \index[scripture]{Psalms!Psa 056:04}\index[scripture]{Psalms!Psa 056:10} (Psalm 56:4, 10) 
    \item The \textbf{Evil} \index[scripture]{Psalms!Psa 056:05}(Psalm 56:5) 
    \item The \textbf{Empathy} \index[scripture]{Psalms!Psa 056:08}(Psalm 56:8) 
    \item The \textbf{Entreaty} \index[scripture]{Psalms!Psa 056:09}(Psalm 56:9) 
    \item The \textbf{Expectation} \index[scripture]{Psalms!Psa 056:13}(Psalm 56:13) 
\end{compactenum}}

\footnote{\textcolor[rgb]{0.00,0.25,0.00}{\hyperlink{PsalmsTOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/psalms_56.html}{\textcolor[cmyk]{0.99998,1,0,0}{Psalm 56 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{To the chief Musician upon Jonathelemrechokim, Michtam of David, when the Philistines took him in Gath.}\\
\\
\textcolor[cmyk]{0.99998,1,0,0}{Be merciful unto me, O God: for man would swallow me up; he fighting daily oppresseth me.}\footnote{\textbf{Psalm 21:9} - Thou shalt make them as a fiery oven in the time of thine anger: the LORD shall swallow them up in his wrath, and the fire shall devour them.}\footnote{\textbf{Psalm 27:2} - When the wicked, even mine enemies and my foes, came upon me to eat up my flesh, they stumbled and fell.}\footnote{\textbf{Psalm 35:25} - Let them not say in their hearts, Ah, so would we have it: let them not say, We have swallowed him up.}\footnote{\textbf{Psalm 57:3} - He shall send from heaven, and save me from the reproach of him that would swallow me up. Selah. God shall send forth his mercy and his truth.}\footnote{\textbf{Psalm 124:3} - Then they had swallowed us up quick, when their wrath was kindled against us:}
[2] \textcolor[cmyk]{0.99998,1,0,0}{Mine enemies would daily swallow \emph{me} up: for \emph{they} \emph{be} many that fight against me, O thou most High.}\footnote{\textbf{Psalm 54:5} - He shall reward evil unto mine enemies: cut them off in thy truth.}\footnote{\textbf{Psalm 9:2} - I will be glad and rejoice in thee: I will sing praise to thy name, O thou most High.}\footnote{\textbf{Psalm 92:8} - But thou, LORD, art most high for evermore.}\footnote{\textbf{Isaiah 57:15} - For thus saith the high and lofty One that inhabiteth eternity, whose name is Holy; I dwell in the high and holy place, with him also that is of a contrite and humble spirit, to revive the spirit of the humble, and to revive the heart of the contrite ones.}\footnote{\textbf{Daniel 5:18} - O thou king, the most high God gave Nebuchadnezzar thy father a kingdom, and majesty, and glory, and honour:}\footnote{\textbf{Micah 6:6} - Wherewith shall I come before the LORD, and bow myself before the high God? shall I come before him with burnt offerings, with calves of a year old?}
[3] \textcolor[cmyk]{0.99998,1,0,0}{What time \fcolorbox{blue}{bone}{I} am afraid, \fcolorbox{blue}{bone}{I} will trust in thee.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{In God \fcolorbox{blue}{bone}{I} will praise his word, in God \fcolorbox{blue}{bone}{I} have put my trust; \fcolorbox{blue}{bone}{I} will not fear what flesh can do unto me.}\footnote{\textbf{Psalm 27:1} - The LORD is my light and my salvation; whom shall I fear? the LORD is the strength of my life; of whom shall I be afraid?}\footnote{\textbf{Psalm 46:1-2} - God is our refuge and strength, a very present help in trouble. Therefore will not we fear, though the earth be removed, and though the mountains be carried into the midst of the sea;}\footnote{\textbf{Psalm 118:6} - The LORD is on my side; I will not fear: what can man do unto me?}\footnote{\textbf{Isaiah 41:10} - Fear thou not; for I am with thee: be not dismayed; for I am thy God: I will strengthen thee; yea, I will help thee; yea, I will uphold thee with the right hand of my righteousness.}\footnote{\textbf{Hebrews 13:6} - So that we may boldly say, The Lord is my helper, and I will not fear what man shall do unto me.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{Every day they wrest my words: all their thoughts \emph{are} against me for evil.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{They gather themselves together, they hide themselves, they mark my steps, when they wait for my soul.}\footnote{\textbf{Psalm 2:1-3} - Why do the heathen rage, and the people imagine a vain thing? The kings of the earth set themselves, and the rulers take counsel together, against the LORD, and against his anointed, saying, Let us break their bands asunder, and cast away their cords from us.}\footnote{\textbf{Psalm 59:3} - For, lo, they lie in wait for my soul: the mighty are gathered against me; not for my transgression, nor for my sin, O LORD.}\footnote{\textbf{Psalm 71:10} - For mine enemies speak against me; and they that lay wait for my soul take counsel together,}\footnote{\textbf{Job 14:16} - For now thou numberest my steps: dost thou not watch over my sin?}\footnote{\textbf{Job 31:4} - Doth not he see my ways, and count all my steps?}
[7] \textcolor[cmyk]{0.99998,1,0,0}{Shall they escape by iniquity? in \emph{thine} anger cast down the people, O God.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{Thou tellest my wanderings: put thou my tears into thy bottle: \emph{are} \emph{they} not in thy book?}\footnote{\textbf{Psalm 139:16} - Thine eyes did see my substance, yet being unperfect; and in thy book all my members were written, which in continuance were fashioned, when as yet there was none of them.}\footnote{\textbf{Malachi 3:16} - Then they that feared the LORD spake often one to another: and the LORD hearkened, and heard it, and a book of remembrance was written before him for them that feared the LORD, and that thought upon his name.}\footnote{\textbf{Revelation 20:12} - And I saw the dead, small and great, stand before God; and the books were opened: and another book was opened, which is the book of life: and the dead were judged out of those things which were written in the books, according to their works.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{When \fcolorbox{blue}{bone}{I} cry \emph{unto} \emph{thee}, then shall mine enemies turn back: this \fcolorbox{blue}{bone}{I} know; for God \emph{is} for me.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{In God will \fcolorbox{blue}{bone}{I} praise \emph{his} word: in the LORD will \fcolorbox{blue}{bone}{I} praise \emph{his} word.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{In God have \fcolorbox{blue}{bone}{I} put my trust: \fcolorbox{blue}{bone}{I} will not be afraid what man can do unto me.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{Thy vows \emph{are} upon me, O God: \fcolorbox{blue}{bone}{I} will render praises unto thee.}\footnote{\textbf{Psalm 9:1-3} - I will praise thee, O LORD, with my whole heart; I will shew forth all thy marvellous works. I will be glad and rejoice in thee: I will sing praise to thy name, O thou most High. When mine enemies are turned back, they shall fall and perish at thy presence.}\footnote{\textbf{Isaiah 12:1} - And in that day thou shalt say, O LORD, I will praise thee: though thou wast angry with me, thine anger is turned away, and thou comfortedst me.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{For thou hast delivered my soul from death: \emph{wilt} not \emph{thou} \emph{deliver} my feet from falling, that \fcolorbox{blue}{bone}{I} may walk before God in the light of the living?}



